A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-01 example.tex
All labels in example done

\begin{figure}[ht]
  \centering 
\begin{subfigure}{0.42\textwidth}
  \centering
  \includegraphics[width=\textwidth]{a_annotated}
  \vspace*{5ex}
  \caption{ $\mathcal{A}'$ with its associated transition variables in symbolic
  form.}\label{fig:aut_a_annotated}
    %\Description[A 3-state automaton with ]{LONG}
  \vspace*{1.9ex}
\end{subfigure}\hfill%
\begin{subfigure}{0.54\textwidth}
  \centering
  \includegraphics[width=\textwidth]{b_annotated}
  \caption{$\mathcal{B}$ with its associated transition variables in symbolic forms.
  The large number of implicitly existentially quantified
  variables~$x_i$ on
  transitions suggest that this automaton has a more complex structure
  with relation to its (free) target variable representing the string length
  than $\mathcal{A}'$. %The variables used here are fresh, and do not correspond to the
  % ones previously used.
}\label{fig:aut_b_annotated}
    %\Description[SHORT]{LONG}
\end{subfigure}
\caption{The automata after arithmetic simplification.}\label{fig:propagated}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering 
\begin{subfigure}{0.42\textwidth}
  \centering
  \includegraphics[width=\textwidth]{a_annotated}
  \vspace*{5ex}
  \caption{ $\mathcal{A}'$ with its associated transition variables in symbolic
  form.}\label{fig:aut_a_annotated}
    \Description[A 3-state automaton with equations on its edges]{
      A 3-state automaton with a self-loop on any character on the
      initial state labelled 1, a transition on c to the accepting state
      and one on d to a state named D, labelled 0 and 1 respectively,
      then one transition from D to FA, the accepting state on d labelled 1.
      The accepting state has a self-loo labelled $l_A -3$.}
  \vspace*{1.9ex}
\end{subfigure}\hfill%
\begin{subfigure}{0.54\textwidth}
  \centering
  \includegraphics[width=\textwidth]{b_annotated}
  \caption{$\mathcal{B}$ with its associated transition variables in symbolic forms.
  The large number of implicitly existentially quantified
  variables~$x_i$ on
  transitions suggest that this automaton has a more complex structure
  with relation to its (free) target variable representing the string length
  than $\mathcal{A}'$. %The variables used here are fresh, and do not correspond to the
  % ones previously used.
}\label{fig:aut_b_annotated}
    \Description[A 4-state automaton with its transitions annotated
    with equations]{A 4-state automaton with transitions from the initial state to B on b,
    one to A on a, labelled $x_{12}$ and $x_{11}$ respectively. State B has one self-loop
    on c labelled $x_9$, one transition back to the initial state labelled 
    b / $x_{11} + x_{12} - 1$. Finally, B has a transition to the accepting state on c,
    labelled $1 0 x_{11}$. A has one self-loop on c labelled $l_A - x_9 - 2x_{11} - 2x_{12}$,
    and one transition on a to the accepting state labelled $x_{11}$.}
\end{subfigure}
\caption{The automata after arithmetic simplification.}\label{fig:propagated}
\end{figure}
